Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-10-30 manuscript/response_to_reviewers.txt

> Reviewer 1 | 04 Sep 2024 | 01:18
> #1
> This study examines the impact of mesoscale eddies on the metabolome and composition 
> of particulate organic matter in the North Pacific Subtropical Gyre. It fills a gap 
> in previous research by exploring the molecular composition of particulate organic 
> matter. The use both of targeted and untargeted metabolomics mass spectrometry to 
> detect molecules sensitive to environmental perturbation. The study finds that many 
> metabolites track biomass trends. Metabolites linked to eukaryotic phytoplankton are 
> enriched at the deep chlorophyll maximum of cyclonic features, while degradation 
> products are enriched in anticyclones. Additionally, depth variability and vertical 
> displacement of isopycnal layer constrain the importance of mesoscale eddies in 
> shaping particulate matter composition. Based on these results, we can infer the 
> biological communities and biogeochemical processes driven by mesoscale eddies at 
> both spatial and temporal scales. Viewing this complex dynamic process from the 
> chemical molecular scale is a perspective that sets this article apart from other 
> traditional methods in examining the changes in this system.
This is an accurate assessment of the manuscript.

> However, I still have some questions.
> Currently, the process of the entire system seems to be predictable. Although the 
> author has introduced and discussed some gaps, especially from the perspective of 
> chemical composition, and this article provides detailed data and reliable analysis, 
> it is not prominent enough from the perspective of the entire system. Perhaps the 
> transformation from space to time and the use of chemical composition to observe the 
> aging process of vortices is a great highlight. It is very difficult to focus on 
> scale eddies and the ecosystem evolution driven by them using traditional methods. 
> If that's the case, the structure and writing style of the paper may need to be 
> adjusted.
> This article focuses on the differences in chemical composition to understand this 
> process, but I always want to connect it with specific biological processes, such 
> as structural changes in biological communities, primary production rates, 
> zooplankton grazing rates, or bacterial production and respiration rates etc. 
> The author also mentioned these. I don't know if the author can add more relevant 
> evidence or discussion to allow readers to connect with these specific biological 
> groups and/or processes. I know it's difficult to integrate these data together, 
> but relevant discussions are possible.
> We already know that mesoscale eddies are complex and dynamic multidimensional 
> processes. The three-dimensional space combined with the temporal evolution of 
> ecosystem structure and function. The changes in the density surface driven by 
> physics during this process lead to the coupling reaction of physics chemistry 
> biology, which is the main thread. In fact, many other physical biological coupling 
> processes are similar, such as upwelling, internal waves/tides. Using the author's 
> method, I think similar situations can also be seen in such processes.
We have expanded the Discussion to touch on the concerns raised by this reviewer.
Specifically, we have mentioned possible links between the increased sulfonium
compounds in the eddy and DMS production, a hypothesis about the reason why
increased cyclonic biomass was not matched by increased export, and extensive
references to additional manuscripts with relevant data.

### 2024-10-30 manuscript/manuscript.Rmd
Forgot to add the GPC fig to the manuscript

>>>>

![](supplement/comb_gpc_patch.png)

*Supplemental Figure 4: Evidence against phosphorus limitation across the MESO-SCOPE eddy transect. Top row of plots (A) correspond to extracted ion chromatograms for 5 metabolites useful for estimating the phosphorus stress of an environment, colored by the depth from which the sample was taken. Middle row of plots shows the integrated peak area for each metabolite across the 11 stations of the transect with sub-panels for each depth independently, with each point colored by the corrected sea level anomaly (SLA). Bottom row of plots shows the ratio of choline to phosphocholine (left) and choline to glycerophosphocholine (right) as a function of corrected SLA with no statistically significant trend visible at any of the three depths.*
